Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-07-11 Paper/paper.tex
description of new lambda median plots

So far we have discussed individual realizations of NSBH populations. The 
underlying stochasticity of the population generation process makes it
difficult to draw generalized inferences (from a single realization) about the
measurability of $\lambdans$. We mitigate this by drawing multiple
realizations of population generation (i.e. multiple identically constructed
populations). Fig.~\ref{fig:TT_LambdaMedian_vs_N_AllInOne} shows the first
results for multiple populations. Lets focus on the left panel first. We
show the median measured value of $\lambdans$ from $100$ independent 
populations with fixed $\lambdans=2000$ as the top set of curves. The one 
highlighted (in green) curve corresponds to the population discussed above.
Similarly, we generate sets of $100$ populations with $\lambdans=500-1500$, and
show the median measured $\lambdans$ as four distinct groups of curves in
Fig.~\ref{fig:TT_LambdaMedian_vs_N_AllInOne} (with the single highlighted
curve in each group corresponding to
Fig.~\ref{fig:TT_Lambda_vs_N_L800_CI90_0}-\ref{fig:TT_Lambda_vs_N_CI90_0}).
Dash-dotted horizontal lines demarcate $\pm50\%$ error intervals around
the true $\lambdans$ values. All of these populations are drawn under
paradigm A (i.e. with BH masses allowed to sample the mass-gap that spans
$2-5M_\odot$).
% 
From the figure, we can conclude with a high likelihood that our measured
$\lambdans$ values will be within $10\%$ of the real value after about
$20$ events for less deformable neutron stars with $\lambdans\leq 1000$,
and in as few as $10$ events for more deformable stars with
$\lambdans\geq 1500$.
% 
The results discussed in Fig.~\ref{fig:TT_Lambda_vs_N_L800_CI90_0},
\ref{fig:TT_Lambda_vs_N_CI90_0} and the left panel
of Fig.~\ref{fig:TT_LambdaMedian_vs_N_AllInOne} all apply to the parameter distribution spanned by 
the grid G. This distribution has $\mbh$ as low as $2.7M_\odot$ (i.e. $q=2$).
Given that disruptive signatures are strongest for small $\mbh$, we now
investigate an alternate paradigm~\footnote{We denote our standard paradigm
which does not respect the mass-gap as paradigm A; with paradigm B being
the scenario where no black hole masses fall within the mass gap.}
with $\mbh\geq 5M_\odot$, consistent
with the ``mass-gap'' suggested by astronomical observations~\cite{Bailyn:1997xt,
Kalogera:1996ci,Kreidberg:2012,Littenberg:2015tpa}
% 
The right panel of the figure is identical to the left panel, but drawn under
population paradigm B (no BHs alloewd within the mass-gap). Under this
paradigm, we expectedly find that information accumulation is slower. It would
take $20-40$ detections with $\rho\geq10$ under this paradigm, for our (median)
measured $\lambdans$ to lie within $10\%$ of the true value (fewer for 
more deformable NSs).
% % 
% This is a promising deduction, as one might expect to see $\mathcal{O}(10)$
% events over a few years' timescale with design aLIGO~\cite{Abadie:2010cfa}.

>>>>

So far we have discussed individual realizations of NSBH populations. The 
underlying stochasticity of the population generation process makes it
difficult to draw generalized inferences (from a single realization of an
NSBH population) about the measurability of $\lambdans$. In order to mitigate
this, we discuss ensembles of population draws next. In
Fig.~\ref{fig:TT_LambdaMedian_vs_N_AllInOne} we show the measured
({median}) $\lambdans$ as a function of the number of observed
events, for four population ensembles, with a hundred population draws
in each ensemble. Lets focus on the {\it top left} panel first. In it, we
show the measured (median) $\lambdans$ for all populations in four ensembles,
with true $\lambdans=\{2000,1500,1000,500\}$ from top to bottom.
Populations highlighted in color are simply those that we discussed in
Fig.~\ref{fig:TT_Lambda_vs_N_CI90_0}. Dash-dotted horizontal lines
demarcate $\pm10\%$ error intervals around the true $\lambdans$ values.
The panel just below it shows the range of $\lambdans$ that encloses the
median measured $\lambdans$ for $90\%$ of the populations in {\it each}
ensemble. In other words, this panel shows the range of $\lambdans$ within which
the median measured $\lambdans$ value for $90\%$ of NSBH populations is
expected to lie. From these panels, we conclude that our measured $\lambdans$
values will be within $10\%$ of the {\it true} value after $\sim 25$
detections of less deformable neutron stars ($\lambdans\leq 1000$), or
after as few as $15$ detections of more deformable neutron stars
($\lambdans\geq 1500$).
% 
The results discussed in Fig.~\ref{fig:TT_Lambda_vs_N_L800_CI90_0},
\ref{fig:TT_Lambda_vs_N_CI90_0} and the left two panels
of Fig.~\ref{fig:TT_LambdaMedian_vs_N_AllInOne} apply to the parameter
distribution spanned by the grid G. This distribution allows for $\mbh$
as low as $2.7M_\odot$ (i.e. $q=2$).
Given that disruptive signatures are strongest for small $\mbh$, we now
investigate an alternate paradigm~\footnote{We denote our standard paradigm
which does not respect the mass-gap as paradigm A; with paradigm B being
the scenario where no black hole masses fall within the mass gap $2-5M_\odot$.}
with $\mbh\geq 5M_\odot$, consistent
with the ``mass-gap'' suggested by astronomical observations~\cite{Bailyn:1997xt,
Kalogera:1996ci,Kreidberg:2012,Littenberg:2015tpa}
% 
Both right panels of the figure are identical to their corresponding left
panels, but drawn under population paradigm B. Under this paradigm, we
expectedly find that information accumulation is much slower. It would
take $25-40$ detections with $\rho\geq10$ under this paradigm, for our (median)
measured $\lambdans$ to converge within $10\%$ of its true value.
% % 
% This is a promising deduction, as one might expect to see $\mathcal{O}(10)$
% events over a few years' timescale with design aLIGO~\cite{Abadie:2010cfa}.
